Covariate analysis of ROSMAP RNASeq

### 2016-05-06 code/Rmd/Mayo_Cerebellum_RNASeq.Rmd

### Data preprocessing
```{r preprocess_data, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA <- METADATA %>%
  dplyr::filter(!(SampleID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER")))
```
Following five samples were considered outliers and removed 742\_CER, 11386\_CER, 11311\_CER, 1923\_CER, 11477\_CER, based on the eucledian distance from other samples and/or seperated on the first 2 PC's
```{r preprocess_data1}
indToRetain = intersect(METADATA$SampleID, colnames(COUNT))

>>>>

### Data preprocessing
```{r preprocess_data, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging", "Pathologic_Aging", METADATA$Diagnosis)
METADATA <- METADATA %>%
  dplyr::filter(!(SampleID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER")))
```
Following five samples were considered outliers and removed 742\_CER, 11386\_CER, 11311\_CER, 1923\_CER, 11477\_CER, based on the eucledian distance from other samples and/or seperated on the first 2 PC's
```{r preprocess_data1}
indToRetain = intersect(METADATA$SampleID, colnames(COUNT))

### 2016-05-06 code/Rmd/ROSMAP_RNASeq.Rmd

COVARIATES.tmp = data.matrix(COVARIATES)
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
```
```{r decompse.normalise.data2, fig.height=8, fig.width=16, results='asis'}
tree = hclust(as.dist(t(EXPR)))
plotDendroAndColors(tree, 
                    colors = labels2colors(COVARIATES.tmp), 
                    dendroLabels = FALSE, 
                    abHeight = 0.80, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES.tmp))
dev.off()
```

>>>>

plotdata <- left_join(plotdata, METADATA) %>%
  dplyr::mutate(Batch = factor(Batch),
                age_death = as.numeric(age_death),
                cogdx = factor(cogdx))

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Batch, shape=cogdx, size=age_death))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= Sampleid), size=4, hjust=1)
p <- p + xlab(paste0('PC1(',round((PC$sdev^2/sum(PC$sdev^2))[1]*100),'%)'))
p <- p + ylab(paste0('PC2(',round((PC$sdev^2/sum(PC$sdev^2))[2]*100),'%)'))
p

COVARIATES.tmp = data.matrix(COVARIATES)
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
```
```{r decompse.normalise.data2, fig.height=8, fig.width=16, results='asis'}
tree = hclust(as.dist(t(EXPR)))
plotDendroAndColors(tree, 
                    colors = labels2colors(COVARIATES.tmp), 
                    dendroLabels = FALSE, 
                    abHeight = 5, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES.tmp))
dev.off()
```
